---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
if(!exists("activity.csv"))unzip("activity.zip")
activity_data <- read.csv("activity.csv",na.strings="NA")
```


## What is mean total number of steps taken per day?
Making a histogram of the total number of steps taken each day, ignoring NA values
```{r}
total<-tapply(activity_data$steps,activity_data$date,sum)
barplot(total)
```

The **mean** and the **median** of total number of steps taken per day
```{r totalstepsmean}
meanNumber<-tapply(activity_data$steps,activity_data$date,mean)
medianNumber<-tapply(activity_data$steps,activity_data$date,median)
meanNumber
medianNumber
```

## What is the average daily activity pattern?
Time series plot of 5-minute interval and the average number of steps taken, avergaed across all days

```{r}
avgdata<-aggregate(x=list(steps=activity_data$steps),by=list(interval=activity_data$interval),FUN = mean, na.rm = T)
plot(avgdata$interval,avgdata$step,type="l")
```
The maximun number of steps on 5-minute interval on average across all the days
```{r maxStep}
maxSteps <- avgdata[which.max(avgdata$steps),1]
```
## Imputing missing values
sum of missing
```{r}
sum(is.na(activity_data))
```
Replacing strategy is to replace the NA with the mean of the interval for that day
```{r}
rnwm <- function(steps, interval){
  result <- NA
  if(!is.na(steps))
    result<-c(steps)
  else
    result<-(avgdata[avgdata$interval==interval,"steps"])
  result
}
activity_data.replaced <- activity_data
activity_data$steps <- mapply(rnwm, activity_data.replaced$steps, activity_data.replaced$interval)
activity_data.replaced.totalsteps <- tapply(activity_data.replaced$steps, activity_data.replaced$date, FUN=sum)

```
Plotting histogram on the newly created dataset, reporting the **mean** and the **median** total number of steps taken each day. 
```{r}
barplot(activity_data.replaced.totalsteps)
#mean
mean(activity_data.replaced.totalsteps)
#median
median(activity_data.replaced.totalsteps)
```
## Are there differences in activity patterns between weekdays and weekends?
```{r}
weekday <- function(date){
  day<- weekdays(date)
  if (day %in% c("星期一","星期二","星期三","星期四","星期五"))
    return ("weekday")
  else if(day %in% c("星期六","星期日"))
    return("weekend")
  else stop("invalid date")
}
activity_data.replaced$date <- as.Date(activity_data.replaced$date)
activity_data.replaced$day <- sapply(activity_data.replaced$date,FUN=weekday)
avgwd <- aggregate(steps~interval+day,data = activity_data.replaced, mean)
par(mfrow=c(2,1))
with(subset(avgwd, day == "weekday"), plot(interval, steps,type = "l",col="blue",main="weekday"))
with(subset(avgwd, day == "weekend"), plot(interval, steps,type = "l",col="blue",main="weekend"))
```
